3D Magnetic modelling of ellipsoidal bodies

### 2017-03-15 manuscript/manuscript.tex
modify small parts of text and review the mesher for fatiando

Then, given the orientation angles $\varepsilon$, $\zeta$, and $\eta$ (Fig. \ref{fig:orientation-angles}a and Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
\ref{eq:delta}), we define the unit vectors

@@

(i.e., $a > b = c$), these unit vectors may be given by \citep{clark1986}:

@@

\citet{emerson1985} also calculate the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
and $\mathbf{v}_{3}$ by using Eqs. \ref{eq:v1_triaxial_prolate},

@@

Finally, the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$
for oblate ellipsoids (i.e., $a < b = c$) may be calculated as follows:

@@

@@

Consider a magnetized ellipsoid immersed in
a uniform inducing magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$)
given by
\begin{equation}
\mathbf{H}_{0} = \| \mathbf{H}_{0} \| \left[
\begin{array}{c}
\cos I \: \cos D \\
\cos I \: \sin D \\
\sin I
\end{array}
\right] \: ,
\label{eq:H0}
\end{equation}
where $\| \cdot \|$ denotes the Euclidean norm (or 2-norm) and
$D$ and $I$ are respectively, the declination and inclination of the 
local-geomagnetic field in the main coordinate system
(Fig. \ref{fig:orientation-angles}a).
This field represents the main component of the
Earth's magnetic field, which is usually assumed to be generated
by the Earth's liquid core.
In the absence of conduction currents, 
the total magnetic field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (Eqs. \ref{eq:A} and 
\ref{eq:coord_transformation}) of a point referred to the main 
coordinate system is defined as follows \citep{sharma1966, 
eskola1980, reitz1992, sttraton2007}:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla V(\mathbf{r}) \: ,
\label{eq:H}
\end{equation}
where the second term is the negative gradient of 
the magnetic scalar potential $V(\mathbf{r})$ given by:
\begin{equation}
V(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{\vartheta} 
\mathbf{M}(\mathbf{r}^{\prime})^{\top} 
\nabla \left(
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:V-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $\vartheta$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ and 
$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
(in $\unit{Am^{-1}}$).
Eq. \ref{eq:V-potential} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body
\citep{dubois1896, reitz1992, sttraton2007}.

Based on \citeauthor{maxwell1873}'s postulate, let us
assume that the body has a uniform magnetization given by
\begin{equation}
\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
\label{eq:M-KH}
\end{equation}
where $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field 
at any point within the body and $\mathbf{K}$ is a 
constant and symmetrical 2nd-order tensor representing the 
magnetic susceptibility of the body. 
This is a good approximation for bodies at room temperature,
subjected to an inducing field $\mathbf{H}_{0}$ with 
strength $\leq 1$ \unit{mT} \citep{rochette1992}.
In this case, the susceptibility tensor $\mathbf{K}$ is commonly
represented, in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
as follows:
\begin{equation}
\mathbf{K} = \mathbf{U}
\left[ \begin{array}{ccc}
k_{1} & 0 & 0 \\
0 & k_{2} & 0 \\
0 & 0 & k_{3} 
\end{array} \right] \mathbf{U}^{\top} \: ,
\label{eq:K}
\end{equation}
where $k_{1} > k_{2} > k_{3}$ are the 
\textit{principal susceptibilities} and $\mathbf{U}$ is
an orthogonal matrix whose columns $\mathbf{u}_{i}$,
$i = 1, 2, 3$, are unit vectors called 
\textit{principal directions}.
The unit vectors $\mathbf{u}_{i}$ may be defined
similarly to $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
and $\mathbf{v}_{3}$ (Eqs. \ref{eq:v1_triaxial_prolate},
\ref{eq:v2_triaxial_prolate}, \ref{eq:v3_triaxial_prolate},
\ref{eq:v1_oblate}, \ref{eq:v2_oblate}, and \ref{eq:v3_oblate}),
by a given set of orientation angles $\varepsilon$, $\zeta$,
and $\eta$ (Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
\ref{eq:delta}).

>>>>

Then, given the orientation angles $\varepsilon$, $\zeta$, and $\eta$ 
(Fig. \ref{fig:orientation-angles}a), we define the auxiliary angles 
$\alpha$, $\gamma$ and $\delta$ (Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
\ref{eq:delta}) and, finally, the unit vectors

@@

(i.e., $a > b = c$), we opted for defining these unit vectors 
by following \citet{clark1986}:

@@

\citet{emerson1985} calculated the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
and $\mathbf{v}_{3}$ similarly by using Eqs. \ref{eq:v1_triaxial_prolate},

@@

Finally, we define the unit vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
and $\mathbf{v}_{3}$ for oblate ellipsoids (i.e., $a < b = c$) as follows:

@@

This approach is very similar to that presented by \citet{emerson1985}.

@@

Consider a magnetized ellipsoid immersed in
a uniform inducing magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$)
given by
\begin{equation}
\mathbf{H}_{0} = \| \mathbf{H}_{0} \| \left[
\begin{array}{c}
\cos I \: \cos D \\
\cos I \: \sin D \\
\sin I
\end{array}
\right] \: ,
\label{eq:H0}
\end{equation}
where $\| \cdot \|$ denotes the Euclidean norm (or 2-norm) and
$D$ and $I$ are respectively, the declination and inclination of the 
local-geomagnetic field in the main coordinate system
(Fig. \ref{fig:orientation-angles}a).
This field represents the main component of the
Earth's magnetic field, which is usually assumed to be generated
by the Earth's liquid core.
In the absence of conduction currents, 
the total magnetic field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}) 
of a point referred to the main 
coordinate system is defined as follows \citep{sharma1966, 
eskola1980, reitz1992, sttraton2007}:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla V(\mathbf{r}) \: ,
\label{eq:H}
\end{equation}
where the second term is the negative gradient of 
the magnetic scalar potential $V(\mathbf{r})$ given by:
\begin{equation}
V(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{\vartheta} 
\mathbf{M}(\mathbf{r}^{\prime})^{\top} 
\nabla \left(
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:V-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $\vartheta$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ and 
$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
(in \unit{Am^{-1}}).
Eq. \ref{eq:V-potential} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body
\citep{dubois1896, reitz1992, sttraton2007}.

Based on \citeauthor{maxwell1873}'s postulate, let us
assume that the body has a uniform magnetization given by
\begin{equation}
\mathbf{M} = \mathbf{K} \, \mathbf{H}^{\dagger} \: ,
\label{eq:M-KH}
\end{equation}
where $\mathbf{H}^{\dagger}$ is the resultant uniform magnetic field 
at any point within the body and $\mathbf{K}$ is a 
constant and symmetrical 2nd-order tensor representing the 
magnetic susceptibility of the body. 
This is a good approximation for bodies at room temperature,
subjected to an inducing field $\mathbf{H}_{0}$ with 
strength $\leq 10^{-3} \mu_{0}^{-1}$ \unit{A \, m^{-1}} \citep{rochette1992},
where $\mu_{0}$ represents the magnetic constant (in \unit{H \, m^{-1}}).
In this case, the susceptibility tensor $\mathbf{K}$ is commonly
represented, in the main coordinate system (Fig. \ref{fig:orientation-angles}a),
as follows:
\begin{equation}
\mathbf{K} = \mathbf{U}
\left[ \begin{array}{ccc}
k_{1} & 0 & 0 \\
0 & k_{2} & 0 \\
0 & 0 & k_{3} 
\end{array} \right] \mathbf{U}^{\top} \: ,
\label{eq:K}
\end{equation}
where $k_{1} > k_{2} > k_{3}$ are the 
\textit{principal susceptibilities} and $\mathbf{U}$ is
an orthogonal matrix whose columns $\mathbf{u}_{i}$,
$i = 1, 2, 3$, are unit vectors called 
\textit{principal directions}.
The unit vectors $\mathbf{u}_{i}$ may be defined
similarly to $\mathbf{v}_{1}$, $\mathbf{v}_{2}$,
and $\mathbf{v}_{3}$ (Eqs. \ref{eq:v1_triaxial_prolate},
\ref{eq:v2_triaxial_prolate}, \ref{eq:v3_triaxial_prolate},
\ref{eq:v1_oblate}, \ref{eq:v2_oblate}, and \ref{eq:v3_oblate}),
by a given set of orientation angles $\varepsilon$, $\zeta$,
and $\eta$ (Eqs. \ref{eq:alpha}, \ref{eq:gamma}, and
\ref{eq:delta}).
